Supplemental Information B: Full Annotated Analysis and Reproducible Code

### 2021-10-08 PreregristrationS3/PreregistrationAOT-M.Rmd
feedback LFB 1/n

---
title           : "Psychological Needs During Intergroup Contact: Young Medical Professionals Sample"
shorttitle      : "Preregistration: Needs During Intergroup Contact"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name        : Jannis Kreienkamp
    affiliation : "1,2"
  - name        : Maximilian Agostini
    affiliation : "1,2"
  - name        : Laura Bringmann
    affiliation : "1,2"
  - name        : Peter de Jonge
    affiliation : "1,2"
  - name        : Kai Epstude
    affiliation : "1,2"
affiliation:
  - id          : 1
    institution : University of Groningen, Department of Psychology
  - id          : 2
    institution : Author order to be discussed; currently alphabetic by last name.
bibliography: references.bib
csl: apa.csl
biblio-style: "apalike" 
output: 
  prereg::cos_prereg:
    citation_package: natbib
editor_options: 
  chunk_output_type: console
---

@@

In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group [@Hewstone1996; @Pettigrew1998]. A key condition for these contact benefits, has been that the interaction is indeed perceived as positive --- making the interaction quality a crucial mechanism of inter-group contact [e.g., @MacInnis2015]. It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact [Allport's Optimal Contact conditions, @Allport1954b]. And indeed a major meta-analytic review showed, that intergroup contact benefits were larger when Allport's conditions were met. However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met.But they don't discuss Allport's conditions. It, thus, remains unclear why exactly Allport's conditions work and whether there might be an underlying psychological mechanism at play.

@@

The data was collected as part of a larger collaboration on daily intergroup relations. The researchers have had no direct access to the data, as the data was collected using an automated system using the FormR framework [@Arslan2020].

@@

1. Contact Hypothesis
    a. Correlation: $r_{InteractionFrequency, OutgroupAttitudes} \neq 0$
    a. T-test: $\mu_{OutgroupInteraction} > \mu_{IngroupInteraction}$ (to build confidence in the persistence of the contact effect, we additionally compare the attitudes after an outgroup interaction to attitudes after no outgroup interaction (i.e., including instances where participants had no interaction at all).)
    a. Regression: $Attitude \sim AverageContactFreq \times AverageContactQual$
1. Allport's Conditions
    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}AllportConditions_{ij} + u_{oj} + r_{ij}$
    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}AllportConditions_{ij} + \gamma_{20}InteractionQuality_{ij} + u_{oj} + r_{ij}$

        with $u_{oj} \sim \mathcal{N}(0,\tau^2_{00})$ and $r_{ij} \sim \mathcal{N}(0,\sigma^2)$
1. Key Need Fulfillment
    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + u_{oj} + r_{ij}$
    a. Regression: $InteractionQuality_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + u_{oj} + r_{ij}$
    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + \gamma_{20}InteractionQuality_{ij} + u_{oj} + r_{ij}$
    a. Regression: $Attitude_{ij} \sim KeyNeedFulfill_{ij} \times OutgroupInteraction_{ij}$
    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + \gamma_{20}Autonomy_{ij} + \gamma_{30}Competence_{ij} + \gamma_{40}Relatedness_{ij} + u_{oj} + r_{ij}$

        with $u_{oj} \sim \mathcal{N}(0,\tau^2_{00})$ and $r_{ij} \sim \mathcal{N}(0,\sigma^2)$
1. Comparison with Allport's Conditions
    a. Model Comparison: $AIC_{KeyNeedModel} > AIC_{AllportModel}$
    a. Regression: $Attitude_{ij} \sim \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ij} + \gamma_{20}AllportConditions_{ij} + u_{oj} + r_{ij}$

        with $u_{oj} \sim \mathcal{N}(0,\tau^2_{00})$ and $r_{ij} \sim \mathcal{N}(0,\sigma^2)$

>>>>

---
title           : "Psychological Needs During Intergroup Contact: Young Medical Professionals Sample"
shorttitle      : "Preregistration: Needs During Intergroup Contact"
date            : "`r Sys.setlocale('LC_TIME', 'C'); format(Sys.time(), '%d\\\\. %B %Y')`"
author: 
  - name        : Jannis Kreienkamp
    affiliation : "1"
  - name        : Maximilian Agostini
    affiliation : "1"
  - name        : Laura Bringmann
    affiliation : "1"
  - name        : Peter de Jonge
    affiliation : "1"
  - name        : Kai Epstude
    affiliation : "1"
affiliation:
  - id          : 1
    institution : University of Groningen, Department of Psychology
bibliography: "../references.bib"
csl: apa.csl
biblio-style: "apalike" 
output: 
  prereg::cos_prereg:
    citation_package: natbib
editor_options: 
  chunk_output_type: console
---

@@

In its most essential interpretation, the intergroup contact hypothesis postulates that frequent and positive contact with an out-group reduces prejudice and increases favorable attitudes towards the other group [@Hewstone1996; @Pettigrew1998]. A key condition for these contact benefits, has been that the interaction is perceived as positive --- making the interaction quality a crucial mechanism of inter-group contact [e.g., @MacInnis2015]. It is widely accepted that equal status, common goals, collaboration, and structural support during the interaction form the optimal conditions for a positive contact [Allport's Optimal Contact conditions, @Allport1954b]. And indeed a major meta-analytic review showed, that intergroup contact benefits were larger when Allport's conditions were met. However, the meta-analysis also showed that contact resulted in more positive intergroup relations even when Allport's conditions were not met. It, thus, remains unclear why exactly Allport's conditions work and whether there might be an underlying psychological mechanism at play.

@@

The data was collected as part of a larger collaboration on daily intergroup relations. The researchers have had no direct access to the data, as the data was collected using an automated system using the FormR framework [@Arslan2020]. The data were then downloaded and stored securely on an encrypted device until the eventual data analysis. None of the researchers have accessed the data thus far.

@@

We will use a sequential analysis strategy in line with our proposed hypotheses. Given the nested structure of much of our data we test many of our hypotheses using a multilevel approach, where $y_{ti}$ denotes the response at measurement occasion $t$ ($t = 1, ...,T_i$, level 1) for individual $i$ ($i = 1, ..., n$, level 2). It should be noted that we will follow a hierarchical regression approach. We follow the common three-step procedure [e.g., @Bliese2013]:

1. Contact Hypothesis
    a. Correlation: $r_{InteractionFrequency, OutgroupAttitudes} \neq 0$
    a. T-test: $\mu_{0utgroupInteraction} > \mu_{IngroupInteraction}$ (to build confidence in the persistence of the contact effect, we additionally compare the attitudes after an outgroup interaction to attitudes after no outgroup interaction (i.e., including instances where participants had no interaction at all).)
    a. Regression: $Attitude = AverageContactFreq \times AverageContactQual$
1. Allport's Conditions
    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}AllportConditions_{ti} + u_{0i} + u_{1i} + e_{ti}$
    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}AllportConditions_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + u_{1i} + e_{ti}$

        with $\begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix}$ and $e_{ti} \sim \mathcal{N}(0,\sigma^2)$
1. Key Need Fulfillment
    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}$
    a. Regression: $InteractionQuality_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + u_{0i} + u_{1i} + e_{ti}$
    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}InteractionQuality_{ti} + u_{0i} + u_{1i} + e_{ti}$
    a. Regression: $Attitude_{ti} = KeyNeedFulfill_{ti} \times OutgroupInteraction_{ti} + u_{0i} + u_{1i} + e_{ti}$
    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}Autonomy_{ti} + \gamma_{30}Competence_{ti} + \gamma_{40}Relatedness_{ti} + u_{0i} + u_{1i} + e_{ti}$

        with $\begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix}$ and $e_{ti} \sim \mathcal{N}(0,\sigma^2)$
1. Comparison with Allport's Conditions
    a. Model Comparison: $AIC_{KeyNeedModel} > AIC_{AllportModel}$
    a. Regression: $Attitude_{ti} = \gamma_{00} + \gamma_{10}KeyNeedFulfill_{ti} + \gamma_{20}AllportConditions_{ti} + u_{0i} + u_{1i} + e_{ti}$

        with $\begin{bmatrix} u_{0i}\\ u_{1i}\end{bmatrix} \sim \mathcal{N}(0,\Omega_u): \Omega_u=\begin{bmatrix} \tau_{0}^2 & \\ \tau_{01} & \tau_{1}^2 \end{bmatrix}$ and $e_{ti} \sim \mathcal{N}(0,\sigma^2)$
